---
output:
  html_document:
    css: extras/styles.css
---

## Using Child Docs 
  
Another method to keep all your code organized is to use child documents. Here is how the parent .Rmd file of this markdown document is set up. Notice that the `{.tabset}` called in the parent .Rmd flows downstream to child .Rmd files. 
  
````{verbatim, lang = "md"}
---
title: "Automating Interactive R Markdown Reports"
output:
  html_document:
    css: extras/styles.css
    includes:
      in_header: extras/header-logo.html
---

```{r, include=FALSE, echo=FALSE}
sys.source("extras/setup.R", envir = knitr::knit_global())
```
This R Markdown document is a quick example of how interactive html output can be automated and organized. I'll use the spotifyr package to pull in some simple data and make quick charts as an example for creating tabs and pills, using child docs, and utilizing Markdown to generate content programmatically.  
***

# {.tabset}

```{r, child=c('tab-1-tabs/tabs.Rmd', 'tab-2-pills/pills.Rmd', 'tab-3-child/child.Rmd', 'tab-4-auto/auto.Rmd', 'tab-5-demo/demo.Rmd')}
```
````
  
Also notice the `sys.source("extras/setup.R", envir = knitr::knit_global())` command. This can be used to load packages, authenticate the spotifyr api connection, set knitr options, etc. all in one place and applied globally. 

```{r setup, eval=FALSE}

library(tidyverse)
library(ggplot2)
library(patchwork)
library(spotifyr)
library(ggthemes)
library(flextable)
options(knitr.duplicate.label = "allow")
access_token <- get_spotify_access_token()

```

  
  


